Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-03 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
the the arreglado

The ES-I platform has been programmed to employ a 
collaborative methodology for performing fitness assignment. 
Several registered users assign a quality assessment to a single
phenotype and then an aggregated fitness value is calculated,
depending on the rating (from 1 to 5 stars) by each particular user,  
resulting in a many-to-many relationship between users and
phenotypes. Other components or users of the systems can 
query this user-phenotype relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular phenotype, or the the user with more participation 
\cite{picbreeder}.
In order to do this, metadata about phenotypes 
must be permanently stored, even
if they are no longer in the active population.

>>>>

The ES-I platform has been programmed to employ a 
collaborative methodology for performing fitness assignment. 
Several registered users assign a quality assessment to a single
phenotype and then an aggregated fitness value is calculated,
depending on the rating (from 1 to 5 stars) by each particular user,  
resulting in a many-to-many relationship between users and
phenotypes. Other components or users of the systems can 
query this user-phenotype relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular phenotype, or the user with more participation 
\cite{picbreeder}.
In order to do this, metadata about phenotypes 
must be permanently stored, even
if they are no longer in the active population.
